---
title: ssh-dynconf
output:
  github_document
---

```{r, echo=FALSE,include=FALSE}
# Make sure colors from tput are used correctly in the output
options(crayon.enabled = TRUE)
knitr::knit_hooks$set(output = function(x, options) {
  paste0(
  #   "<svg fill=\"none\" viewBox=\"0 0 600 300\" width=\"600\" height=\"300\" xmlns=\"http://www.w3.org/2000/svg\">",
  # "<foreignObject width=\"100%\" height=\"100%\">",
    '<pre class="r-output">',
    paste0(
      "<code>",
      paste0(
        fansi::to_html(
          x =
            htmltools::htmlEscape(x),
          warn = FALSE,
          carry = FALSE
        ),
        collapse = "  \n"
      ),
      "</code>",
      collapse = "\n"
    ),
    "</pre>"
    # "</foreignObject>",
# "</svg>"
  )
})
num_colors <- function(forget = TRUE) 256
library(crayon)
assignInNamespace("num_colors", num_colors, pos = "package:crayon")
Sys.setenv("TERM" = "dumb")

print_help <-
  function(x) {
    cat(
      system(
        paste0(
          "/usr/bin/env bash -c \"source ./ssh-dynconf-init && ",
      x,
      " --help\""
      ), 
      intern = TRUE),
      sep =
        "\n"
    )
  }
```

Functions for dynamically generating / modifying ssh config files and availability checks ssh hosts

## Core functions

### Check ssh hosts' availability

#### `ssh_host_available`

```{r, eval=TRUE, echo=FALSE,include=TRUE,comment=""}
print_help("ssh_host_available")
```

#### `ssh_available_hosts`

```{r, eval=TRUE, echo=FALSE,include=TRUE,comment=""}
print_help("ssh_available_hosts")
```

### Modify ssh config file(s)

#### `ssh_config_update`

```{r, eval=TRUE, echo=FALSE,include=TRUE,comment=""}
print_help("ssh_config_update")
```

## Examples 

The following basic examples how to use `ssh-dynconf` are located in the [`Examples/`](examples/) folder:

```{r, echo=FALSE,include=FALSE}
knitr::knit_hooks$set(output = function(x, options) {
  c(
    '```data',
    paste0(
      paste0(
        x,
        collapse = " \n"
      ),
      collapse = "\n"
    ),
    "```"
  )
})
```


Connecting to a host referred to as `examplehost`
on port `50212`:

```{bash ssh_command,echo=TRUE,eval=FALSE,comment=NA}
ssh -F ssh_config examplehost -p 50212 
```

using a dynamic [configuration](https://man7.org/linux/man-pages/man5/ssh_config.5.html)
can be achieved using a [`ssh_config`](examples/ssh_config) that contains

```{bash ssh_config,echo=FALSE,comment=NA}
cat "examples/ssh_config"
```

If the entered host matches 'examplehost',
a script [make-examplehost-config.sh](examples/make-examplehost-config.sh) is executed, e.g. containing

```{bash ssh_script,echo=FALSE,comment=NA}
cat "examples/make-examplehost-config.sh"
```

to create/modify a configuration file [`examplehost-config`](examples/examplehost-config)
with a conditional hostname for `examplehost`. \
This [`examplehost-config`](examples/examplehost-config) is then included in the 
as configuration in the original
[`ssh_config`](examples/ssh_config).
